
## 2. Datavyu - Mom locomotion pass  
### 2.1 General orientation:
<indent>Screenshot of template</indent><br>
<indent>Column name: `momloc`</indent><br>
<indent>Prompt: `<loc_l-f-.>`</indent><br>

This code captures the times that mom is engaged in locomotion or fell.
<br><br>
Bouts of locomotion are scored as events, where the gray spaces between cells mean the mom is stationary.
<br><br>
Coders are watching/tagging each of these events by marking onset/offset times for the duration of locomotion bouts.
<br><br>
Coders are watching for steps with the feet, the knees, or the bum.
<br><br>
Any other movements that are not initiated from these three body locations is considered to be a transition between postures and is subsumed by stationary, as it is not locomotion.
<br><br>
Bouts that are coded as “.” means that mom is off camera or her legs are off camera, and coder cannot see or infer whether mom is stationary or moving

### 2.2 List of values and definitions
`l` = <div class="videobuttons">
<button size="xs" type="button" data-toggle="collapse" data-target="#coding-locomotion-mom-l">
Locomotion
</button> 
</div> 
<div id="coding-locomotion-mom-l" class="collapse" aria-expanded="false" style="height: 0px;">
```{r child = 'coding_locomotion_mom_l.Rmd'}
```
</div>
<br>
`f` = <div class="videobuttons">
<button size="xs" type="button" data-toggle="collapse" data-target="#coding-locomotion-mom-f">
Fall
</button> 
</div> 
<div id="coding-locomotion-mom-l" class="collapse" aria-expanded="false" style="height: 0px;">
```{r child = 'coding_locomotion_mom_f.Rmd'}
```
</div>
<br>
`.` = <div class="videobuttons">
<button size="xs" type="button" data-toggle="collapse" data-target="#coding-locomotion-mom-null">
Not codable
</button> 
</div> 
<div id="coding-locomotion-mom-null" class="collapse" aria-expanded="false" style="height: 0px;">
```{r child = 'coding_locomotion_mom_null.Rmd'}
```
</div>
<br>


### 2.3 How to code

Set “JUMP-BACK-BY” key to 1 s.
<br><br>
Enable cell highlighting on the controller.
<br><br>
Watch in real time for the mom's movement.
<br><br>
Watch for the feet and knees.
<br><br>
As soon as you see mom's foot/knee lift up off of the ground; hit #5-STOP and then hit “JUMP-BACK-BY” to go back to the timestamp that is just before the lift. 
Then JOG forward by hitting #3-JOGFORWARD until you reach the onset of that cell. If you go too far, you can JOG backward by hitting #1-JOGBACK. 
If you feel that you have either jumped too far back or went too far forward, hold the JOG keys to move in either direction a bit faster. 
Hit ENTER to create a new cell at this Onset.
<br><br>
Now, watch in real time to see when the mom stops moving. 
The Offset is when the mom stops moving for at least 0.5 s (the pause has to look and feel like an actual pause when you are watching in real time; don't simply end a bout of locomotion because there was a 0.5-s pause, especially if it looks like the mom is about to take another step). 
The first frame when the foot/knee stops moving or when the foot settles into its final position is the offset. The same applies to sliding steps.
<br><br>
To set the Offset, use the same rules for mechanics as with the Onset. 
Hit #5-STOP and then hit “JUMP-BACK-BY” to go back to the timestamp that is just before the lift. 
Then JOG forward by hitting #3-JOGFORWARD until you reach the Offset of that cell. 
If you go too far, you can JOG backward by hitting #1-JOGBACK. 
You will likely have to hit the JOG keys numerous times. 
If you feel that you have either jumped too far back or went too far forward, hold the JOG keys to move in either direction a bit faster.
